Legacy Data Confounds Genomics Studies

### 2018-10-23 legacy.tex
small edits

\begin{table}[h]
\begin{tabular}{l  l  l}
                      & \textbf{Repeat}  & \textbf{Non-Repeat}       \\ \cline{2-3} 
\textbf{SNP}  & 2207 & 3839 \\ \cline{2-3} 
\textbf{INDEL} & 750  & 1175 \\ \cline{2-3}
\end{tabular}
\caption{Number of statistically significant variants per category}
\label{sigTable}
\end{table}

@@

The EBV strain was used to transform B-cells from blood samples from the 1kGP into lymphoblastoid cell lines.
This is a commonly used transformation that helps preserve cell lines for long periods of time.
It is unclear what exactly might be causing the association to EBV copy number and the data quality, however, one could speculate that different protocols were used in the cell culturing of certain samples from the 1kGP which might affect the replication of the virus in the cells, or somehow affect the overall quality of the sequencing data produced.
Further investigations in the source of the issue could be done using the raw sequence data from the 1kGP along with the per sample per base quality metrics. \sgcomment{this could be cleaned up}

>>>>

\begin{table}[h]
\begin{tabular}{l  r r}
                      & {Repeat}  & {Non-Repeat}       \\ \hline
{SNP}  & 2207 & 3839 \\  
{INDEL} & 750  & 1175 \\ \hline
\end{tabular}
\caption{Number of statistically significant variants per category}
\label{sigTable}
\end{table}

@@

The EBV strain was used to transform B-cells from blood samples from the 1kGP into lymphoblastoid cell lines.
This is a commonly used transformation that helps preserve cell lines for long periods of time.
It is unclear what exactly might be causing the association to EBV copy number and the data quality, however, one could speculate that different protocols were used in the cell culturing of certain samples from the 1kGP which might affect the replication of the virus in the cells, or somehow affect the overall quality of the sequencing data produced. Given that the bias appears to have been resolved in later stages of the project using updated sequencing platforms, we did not pursue this line of investigation.
